---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bcmixed

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/kzkzmr/bcmixed.svg?branch=master)](https://travis-ci.org/kzkzmr/bcmixed)
<!-- badges: end -->

The bcmixed package provides two categories of important functions:
    bcmarg and bcmmrm. The bcmarg function provides inferences on 
    the marginal model of the mixed effect model with the Box-Cox 
    transformation and the bcmmrm function provides inferences 
    on the model median differences between treatment groups for 
    longitudinal randomized clinical trials. These statistical
    methods are proposed by Maruo et al. (2017, doi:10.1002/sim.6408).

## Installation

You can install the released version of bcmixed from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("bcmixed")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kzkzmr/bcmixed")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(bcmixed)
data(aidscd4)
# Marginal model of mixed model with the Box-Cox transformation
res1 <- bcmarg(cd4 ~ as.factor(treatment) * as.factor(weekc) + age,
       data = aidscd4, time = weekc, id = id)
summary(res1)

# Box-Cox transformation for the baseline
lmd.bl <- bcmarg(cd4.bl ~ 1, data = aidscd4[aidscd4$weekc == 8, ])$lambda
aidscd4$cd4.bl.tr <- bct(aidscd4$cd4.bl, lmd.bl)

# Inference on model median differences between groups at each time point
res2 <- bcmmrm(outcome = cd4, group = treatment, data = aidscd4, time = weekc,
       id = id, covv = c("cd4.bl.tr", "sex"), cfactor = c(0, 1),
       glabel = c("Zid/Did", "Zid+Zal", "Zid+Did", "Zid+Did+Nev"))

# Summarize
print(res2)

summary(res2)

plot(res2, ylab = "CD4+1", xlab = "Week")
```
